Multisensor Architecture for an Intersection Management System

### 2018-05-31 ch3-arch_sys.tex
Added information structure section

The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output. The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from. Three main components of the architecture are defined: communication scheme, data model and  processing blocks.

@@

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.

@@

>>>>

The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output. The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from. Four main components of the architecture are defined: communication scheme, data model, information structure and processing blocks.

@@

The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to. For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.

\subsection{Information Structure}

Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.

\subsubsection{.imscfg file}

For running, the systems requires first a .imscfg file which describes the scenario and the sensors configuration. This information is stored as a JSON object with the properties decribed in table \ref{imscfg_file}.

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c | c|}
\hline
\textbf{Property} & \textbf{Description} \\
\hline
name & Name of the configuration \\
\hline
map & Information of the scene, including map, coordinate system \\ 
 & and region of interest. \\
\hline
cameras & List of camera sensors information \\
\hline
range\_sensors & List of range sensors information \\
\hline
legs & List of legs information \\
\hline
intersection & Information of area of the intersection \\
\hline
\end{tabular}
\caption{Properties in .imscfg JSON file}
\label{imscfg_file}
\end{table}

\subsubsection{data messages and configuration parameters}

In addition to .imscfg file, there are different types of messages and parameters which have its own structure, for example used for sensors configuration or processed data. The table \ref{desc_map} gives a description of the types of information used. A more detailed documentation is given in appendix TODO.

\begin{table}[ht!]
\footnotesize
\centering
\begin{tabular}{|c | p{8cm}|}
\hline
\textbf{Name} & \textbf{Description} \\
\hline
laser\_pol\_msg & Contains a timestamp, an array of N angles and and array of N measurements \\
\hline
laser\_cart\_msg & Contains a timestamp, an array of N (x, y) coordinates \\
\hline
laser\_cfg & Contains position and orientation information, also has a background model for the laser sensor \\
\hline
occgrid\_msg & Contains a timestamp and an occupancy grid in the form of an MxN array \\
\hline
\end{tabular}
\caption{Description of diferent types of messages and parameters used}
\label{desc_map}
\end{table}

@@

Additionaly, there are included some tools and generic blocks used for dataset reading, data visualization and interactive control.
